Distributed Environment for Auctioning Virtual Power System Resources

### 2022-02-04 other/paper-aicts-chekan.tex
Update

After the first auction pass, when the objects are pre-assigned, participants can refuse a certain number of their lots, putting them on the second pass of the auction, along with those that were unplaced on the first. In case of refusal of a lot, the participant loses the right to compete for this lot. The value of the refused lots is then determined anew (that is, the bid range is reset to the original one).

At the end of the auction, the results tally is generated to represent information about the ownership of the objects, the bids set on them, and the submitted all-pay bids.

According to the game model described above, a state diagram is drawn, shown in Figure~\ref{fig:1}.

\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{pics/statechart.png}
  \caption{Auction state model}
  \label{fig:1}
\end{figure}

This model allows simultaneous independent draw of several lots. This further increases the dynamics and cognitive complexity of the auction, forcing participants to more carefully coordinate their decisions about the value of the lots to keep pace with the pace of the auction.

The described model is abstract enough and contains almost no binds to the stand domain. Therefore, the model enables solving other tasks related to the distribution of virtual resources. It is also possible to change the model implementation, if necessary, i.e., add additional rules.

@@

To minimize network traffic between levels, atomic state changes (denoted as effects) are transmitted instead of the new state to minimize network traffic between levels. An effect is generated for each event and passed to all child nodes. The full state is transmitted only when the game session is completely restarted and when the child node is reconnected (in future iterations, it is possible to implement persistent caching and full synchronization of such a state).
When considering the game state, the effects are following:
\begin{itemize}
\item the game state change (for example, the start of the auction is the transition from preparation to the active state);
  \item  a pause setting or removing;
  \item  lots rejection start (time limit, the number of lots to reject);
  \item  lot rejection finish (list of lot indices that need to be reset for the second draw);
  \item  a singular lot of state change;
  \item  bids update for a given lot (index, current bid list);
  \item  mid-rejection update (the current list of lots rejected by the participants).
\end{itemize}

>>>>

After the first auction pass, when the objects are pre-assigned, participants can refuse a certain number of their lots, putting them on the second pass of the auction, along those were unplaced on the first. In case of refusal of a lot, the participant loses the right to compete for this lot. The value of the refused lots is then determined anew (that is, the bid range is reset to the original one).

At the end of the auction, the results tally is generated to represent information about the ownership of the objects, the bids set on them, and the submitted all-pay bids.
According to the game model described above, a state diagram is drawn, shown in Figure~\ref{fig:1}.
\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{pics/statechart.png}
  \caption{Auction state model}
  \label{fig:1}
\end{figure}
This model allows simultaneous independent draw of several lots. This further increases the dynamics and cognitive complexity of the auction, forcing participants to more carefully coordinate their decisions about the value of the lots to keep pace with the pace of the auction.

The described model is abstract enough and contains almost no binds to the stand domain. Therefore, the model enables solving other tasks related to the distribution of virtual resources. It is also possible to change the model implementation, if necessary, \emph{i.e}., add additional rules.

@@

To minimize network traffic between levels, atomic state changes (hereafter denoted as \emph{effects}) are transmitted instead of the new state to minimize network traffic between levels. An effect is generated for each event and passed to all child nodes. The full state is transmitted only when the game session is completely restarted and when the child node is reconnected (in future iterations, it is possible to implement persistent caching and full synchronization of such a state).
When considering the game state, the effects are following:
\begin{itemize}
\item the game state change (for example, the start of the auction is the transition from preparation to the active state);
  \item  a pause setting or removing;
  \item  lots rejection start (time limit, the number of lots to reject);
  \item  lot rejection finish (list of lot indices that need to be reset for the second draw);
  \item  a singular lot of state change;
  \item  bids update for a given lot (index, current bid list);
  \item  mid-rejection update (the current list of lots rejected by the participants).
\end{itemize}
